---
title: "Analyis of the #econtwitter hashtag"
author: "Jeffrey Naecker"
output: html_document
---

```{r setup, message = F, include = F}
knitr::opts_chunk$set(message = FALSE)

library(rtweet)
library(ggplot2)
library(dplyr)
library(ggrepel)
library(knitr)
library(kableExtra)
library(stargazer)

theme_set(theme_minimal())
```

I decided to try out the `rtweet` package to access Twitter data easily, and also the `ggrepel` packages to spice up my graphics.  And what better use than a quick analysis of `#econtwitter` itself!

To start, let's download tweets with the `#econtwitter` hashtag.  Let's get a sense of the volume of tweets, by looking at the number posted under this hashtag every day.
It looks like we can only get data going back about one week.

```{r data, cache=TRUE}
tweets <- search_tweets("#econtwitter", n = 1000, include_rts = FALSE)
users <- users_data(tweets)
```

```{r}
tweets %>%
  ts_plot() +
  labs(title = "Tweets tagged with #econtwitter per day", x = "Date", y = "Number of tweets")
```

Who are the most prolific tweeters?  Let's look at the users with the most tweets in the data set.  Let's also check out their total and average retweets and favorites.

```{r}
users <- 
  tweets %>%
  group_by(screen_name) %>%
  summarize(
    n_tweets         = n(),
    favorite_total   = sum(favorite_count),
    retweet_total    = sum(retweet_count),
    favorite_average = mean(favorite_count),
    retweet_average  = mean(retweet_count)
  ) %>%
  left_join(unique(users))

users %>%
  select(screen_name, n_tweets, favorite_total, retweet_total, retweet_average, favorite_average, followers_count) %>%
  arrange(desc(n_tweets)) %>%
  head(10) %>%
  kable() %>%
  kable_styling("hover", full_width = F)
```

We can see that there is quite a lot of variation in the attention that the average tweet gets for different users. Let's plot average retweets against average likes, where each observation is a user.

```{r}
users %>%
  mutate(label = if_else(favorite_average >= 75 | retweet_average >= 15, screen_name, "")) %>%
  ggplot(aes(x = favorite_average, y = retweet_average, label = label)) +
  geom_point() +
  geom_text_repel(point.padding = 0.5) +
  stat_smooth(method = "lm")
```

Unsurprisingly, retweets and favorites are highly correlated.  Let's try to construct a single impact score that takes into account both retweets and favorites.  To see what the right "exchange rate" is between the two, let's use a simple linear regression.  We'll let the level of observation be a tweet, not a user, in this case.

```{r}
model <- 
  tweets %>%
  lm(retweet_count ~ favorite_count, data = .) 

model %>%
  stargazer(type = "text")

coef <- summary(model)$coef[2,1]
```

This says that a favorite is equal to about `r round(coef, 2)` of a retweet.  Let's use this coefficient to create a single "impact index" for all the tweets and users.

```{r}
tweets$impact_index <- coef*tweets$favorite_count + tweets$retweet_count

users <-
  users %>%
  mutate(
    impact_index_average = favorite_average + retweet_average,
    impact_index_total   = n_tweets * impact_index_average
  )
```

Now that we have our index, let's see if which users have the most impact.  We'll graph impact as well as number of tweets. Each point is a user.  I've added labels to the most high-impact tweeters.

```{r}
users %>%
  mutate(label = if_else(impact_index_total >= 180, screen_name, "")) %>%
  ggplot(aes(x = impact_index_total, y = n_tweets, label = label)) +
  geom_point() +
  geom_text_repel() 
```

Finally, let's look at the most imactful single tweets from this data set. Unsurprisingly, the highest-impact tweets are very pro-social in nature, eg announcing a new resource or giving general-interest advice.

```{r}
# most liked tweets
tweets %>%
  arrange(desc(impact_index)) %>%
  select(screen_name, impact_index, retweet_count, favorite_count, text) %>%
  head(3) %>%
  kable() %>%
  kable_styling("hover", full_width = F)
```



